---
title: "Fizzbuzz"
author: "Matt"
date: "2/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains student solutions to the fizzbuzz problem. Students will add to this file using the outline below. Write your name (using three hashtags), then below create an R code block and insert your code. Save the .rmd file, then knit the document to update the html output. Then submit a pull request to merge your changes to the main repository.

### Jeff Kravitz

```{r}
total <- 1
for (i in 2:100) {
  if (i %% 3 == 0) {
    if (i %% 5 == 0) {
      total <- paste(total,"FizzBuzz", sep = ", ")
    }
    else {
      total <- paste(total,"Fizz", sep = ", ")
    }
  }
  else if (i %% 5 == 0) {
    total <- paste(total, "Buzz", sep = ", ")
  }
  else {
    total <- paste(total, i, sep = ", ")
  }
}
print(total)
```

### Matt's Code

```{r,eval=F}
answer <- 1:100 # Creates initial variable of answer of values 1 to 100
for(i in 1:100){ #Recreates loop to alter "answer" where it meets necessary conditions
  if(i%%3 == 0) answer[i] <-"fizz" #Replaces number in "answer" array with "fizz" because it is divisible by 3
  if(i%%5 == 0) answer[i] <-"buzz" #Replaces number in "answer" array with "buzz" because it is divisible by 5
  if(i%%5 == 0 & i%%3 ==0) answer[i] <-"fizzbuzz" #Replaces number in "answer" array with "fizzbuzz" because it is divisible by both 5 and 3
}
print(answer) #prints array of "answer"
```

### Kamal Abdelrahman's Code_p1

```{r}
for (i in c(1:100)){
 if(i%%3 == 0){
  print("Fizz")
 } 
 if(i%%5 == 0){
  print("Buzz")
 }
 if (i%%5 == 0 & i%%3 ==0) {
  print("FizzBuzz")
 }
}
```

### Kamal Abdelrahman's Code_p2
####Minor remix of Crump Code. Was curious to see if the "else if" was necessary. Realized that the as long as the the first "if " is false, function will go to next if until it hits true or it runs out of ifs. Same principle with if then else if statements.
####Also realized that storing the variables and editing them with the if statements is way more accurate than just using if statements. Use the conditions to replace the numbers with "Fizz", "Buzz" or "FizzBuzz" as necessary
```{r}
NumOrWor <- c(1:100)
for (i in c(1:100)){
 if (i%%3 == 0) {
  NumOrWor[i] <- "Fizz"
    } else if(i%%5 == 0) {
        NumOrWor[i] <- "Buzz"
    } else if(i%%5 == 0 & i%%3 ==0) {
        NumOrWor[i] <- "FizzBuzz"
    }
}
print(NumOrWor)
```

